---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/refuge)](https://cran.r-project.org/package=refuge)
[![GitHub tag](https://img.shields.io/github/tag/evanodell/refuge.svg)](https://github.com/evanodell/refuge)
[![](https://cranlogs.r-pkg.org/badges/grand-total/refuge)](https://dgrtwo.shinyapps.io/cranview/)
[![Travis build status](https://travis-ci.org/evanodell/refuge.svg?branch=master)](https://travis-ci.org/evanodell/refuge)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/evanodell/refuge?branch=master&svg=true)](https://ci.appveyor.com/project/evanodell/refuge)
[![Coverage status](https://codecov.io/gh/evanodell/refuge/branch/master/graph/badge.svg)](https://codecov.io/github/evanodell/refuge?branch=master)
[![DOI](https://zenodo.org/badge/129826417.svg)](https://zenodo.org/badge/latestdoi/129826417)



# refuge

`refuge` provides access to the [Refuge Restrooms API](https://www.refugerestrooms.org/api/docs/#!/restrooms) in R.

[Refuge Restrooms](https://www.refugerestrooms.org/) "is a web application that seeks to provide safe restroom access for transgender, intersex, and gender nonconforming individuals." The web application includes a public API, which this package allows access to. The API does not require users to sign up or use a key. For further details on the API or the organisation behind it, see the [API docs](https://www.refugerestrooms.org/api/docs/), or the [Refuge Restrooms homepage](https://www.refugerestrooms.org/).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("evanodell/refuge")
```

## Use

Locating all restrooms close to a given set of coordinates, in this case somewhere in New Jersey:

```{r}
library(refuge)

bathrooms <- rfg_location(lat=39, lng=-75)

tibble::glimpse(bathrooms)

```


Locating all unisex, accessible restrooms in Toronto, using the `rfg_search()` function.

```{r}

toronto <- rfg_search("toronto", accessible = TRUE, unisex = TRUE)

tibble::glimpse(toronto)

```


Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
  By participating in this project you agree to abide by its terms.

Odell E (2018). _refuge: Locate Trans and Intersex-Friendly Toilets_. doi:
10.5281/zenodo.1219900 (URL: http://doi.org/10.5281/zenodo.1219900), R package version
0.1.0, <URL: https://github.com/evanodell/refuge>.

A BibTeX entry for LaTeX users is

```
  @Manual{,
    title = {{refuge}: Locate Trans and Intersex-Friendly Toilets},
    author = {Evan Odell},
    year = {2018},
    note = {R package version 0.1.0},
    doi = {10.5281/zenodo.1219900},
    url = {https://github.com/evanodell/refuge},
  }
```
